---
title: "Beginning to Forecast in R"
author: "Dean Croushore"
date: "Jan 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

First, manipulate the data in Excel and do plots there to be sure it all makes sense.

Note that FRED seems to have an error, reporting values of 0 for M2OWN in the first two months, so delete those in the "data for R" worksheet.

Download the page containing "data for R". Bring it into R.

```{r}
library(readxl)
Data <- read_excel("~/Desktop/FinalPaperR/UpdatedData.xls")
#View(Data)
library(forecast)
```
Now, organize the data as a time series. 
```{r}
DollarIndex <- Data[53:236,9]
DollarIndexts <- ts(data = DollarIndex, start = c(1973,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

NXGDP <- Data[1:236,8]
NXGDPts <- ts(data = NXGDP, start = c(1960,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

FDIGDP <- Data[121:236,7]
FDIGDPts <- ts(data = FDIGDP, start = c(1990,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

IRGDP <- Data[1:236,6]
IRGDPts <- ts(data = IRGDP, start = c(1960,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

ExRate <-Data[85:236,10]
ExRatets <- ts(data = ExRate, start = c(1981,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)
```

Download the package (pastecs), which is Package for Analysis of Space-Time Ecological Series.

Load the pastecs library:

```{r}
library(pastecs)

stat.desc(DollarIndexts)
stat.desc(NXGDPts)
stat.desc(FDIGDPts)
stat.desc(IRGDPts)
stat.desc(ExRatets)
```


