---
title: "ExRate"
author: "Jesse Conway"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
Data <- read_excel("~/Desktop/FinalPaperR/UpdatedData.xls")
#View(Data)
library(forecast)
```

```{r}
ExRate <-Data[85:236,10]
ExRatets <- ts(data = ExRate, start = c(1981,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

ExRate2 <-Data[89:236,10]
ExRate2ts <- ts(data = ExRate2, start = c(1982,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)
```

ARIMA TESTING d = 0:

mean trend:

```{r}
R000mean <- Arima(ExRatets, order = c(0,0,0)) 
summary(R000mean)
RES_mean = residuals(R000mean)
```

BIC = 671.34

linear trend:

```{r}
R000lt <- Arima(ExRatets, order = c(0,0,0), include.drift = TRUE) 
summary(R000lt)
```

BIC = 602.2

trend + seasonal dummies:

```{r}
Sdum <- seasonaldummy(ExRatets)
R000sd <- Arima(ExRatets, order = c(0,0,0), include.drift = TRUE, xreg = Sdum) 
summary(R000sd)

```

BIC = 617.25

trend + seasonal differences:

```{r}
R000sf <- Arima(ExRatets, order = c(0,0,0), seasonal = c(0,1,0), include.drift = TRUE) 
summary(R000sf)
```

BIC = 255.35

compare w/ same sample size:

```{r}
R0002 <- Arima(ExRate2ts, order = c(0,0,0), include.drift = TRUE) 
summary(R0002)
```

BIC = 582.71

best model:

```{r}
RESR00sf <- residuals(R000sf)
```

PAC's/ AC's:

```{r}

Acf(RESR00sf)
Pacf(RESR00sf)

```

mixed?

ARIMA testing:

```{r}
Rma1 <- Arima(ExRatets, order = c(0,0,1), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rma1)
```

BIC = 146.98

```{r}
Rar1 <- Arima(ExRatets, order = c(1,0,0), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rar1)
```

BIC = 122.4

```{r}
Rarma11 <- Arima(ExRatets, order = c(1,0,1), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rarma11)
```

BIC = 124.78

```{r}
Rar2 <- Arima(ExRatets, order = c(2,0,0), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rar2)
```

BIC = 123.86

So, AR(1) is our best model.

White noise?

```{r}
checkresiduals(Rar1)
```

not white noise...!

Forecast: QUESTION (what to forecast on)?

```{r}
plot(forecast(Rar1,h=8))
for011 <- forecast(Rar1, h = 8)
print(for011)
```

ARIMA TESTING d = 1:

Test for a unit root just to see


Let's run the KPSS and ADF tests:

```{r}
Rmean <- Arima(ExRatets, order = c(0,0,0)) 
ndiffs(RES_mean,test="kpss")
ndiffs(RES_mean,test="adf")
```

This implies that there is a unit root, so lets see how taking it out changes the BIC:

mean trend:

```{r}
R010mean <- Arima(ExRatets, order = c(0,1,0)) 
summary(R010mean)
```

BIC = 33.58

linear trend:

```{r}
R010lt <- Arima(ExRatets, order = c(0,1,0), include.drift = TRUE) 
summary(R010lt)
```

BIC = 35.93

trend + seasonal dummies:

```{r}
Sdum2 <- seasonaldummy(ExRatets)
R010sd <- Arima(ExRatets, order = c(0,1,0), xreg = Sdum2) 
summary(R010sd)

```

BIC = 45.03

trend + seasonal differences:

```{r}
R010sf <- Arima(ExRatets, order = c(0,1,0), seasonal = c(0,1,0)) 
summary(R010sf)
```

BIC = 128.81

compare w/ same sample size:

```{r}
R0102 <- Arima(ExRate2ts, order = c(0,1,0)) 
summary(R0102)
```

BIC = 36.43

best model:

```{r}
RESR010mean <- residuals(R010mean)
```

PAC's/ AC's:

```{r}

Acf(RESR010mean)
Pacf(RESR010mean)

```


ARIMA testing:

```{r}
Rima11 <- Arima(ExRatets, order = c(0,1,1)) 
summary(Rima11)
```

BIC = 37.83


```{r}
Rari11 <- Arima(ExRatets, order = c(1,1,0)) 
summary(Rari11)
```

BIC = 37.81

```{r}
Rarima111 <- Arima(ExRatets, order = c(1,1,1)) 
summary(Rarima111)
```

BIC = 40.08

```{r}
Rari21 <- Arima(ExRatets, order = c(2,1,0)) 
summary(Rari21)
```

BIC = 42.79



So, AR(1) is our best model.

White noise?

```{r}
checkresiduals(Rari11)
```

White noise!

Forecast: QUESTION (what to forecast on and how many quarters out)?

```{r}
plot(forecast(Rari11,h=8))
for0112 <- forecast(Rari11, h = 8)
print(for0112)
```


* forecasts 2 years out?

SMOOTHING MODELS:

Plot:

```{r}
library(ggplot2)
autoplot(ExRatets) +
ylab("Chinese US Exchange Rate") + xlab("Year")
```


Simple Smoothing:

```{r}
s1 <- ses(ExRatets, h = 8, level = c(80, 95), alpha = 0.1)
autoplot(s1) +
autolayer(fitted(s1), series="Fitted") +
ylab("Exchange Rate with China") + xlab("Year")
```


```{r}
s2 <- ses(ExRatets, h = 8, level = c(80, 95), alpha = 0.5)
autoplot(s2) +
autolayer(fitted(s2), series="Fitted") +
ylab("Exchange Rate with China") + xlab("Year")
```


```{r}
s3 <- ses(ExRatets, h = 8, level = c(80, 95), alpha = 0.9)
autoplot(s3) +
autolayer(fitted(s3), series="Fitted") +
ylab("Exchage Rate with China") + xlab("Year")
```

```{r}
ss4 <- ses(ExRatets)
 summary(ss4)
 
```

BIC = 375.0936
Alpha = 0.9999


```{r}
s4 <- ses(ExRatets, h = 8, level = c(80, 95))
autoplot(s4) +
autolayer(fitted(s4), series="Fitted") +
ylab("Exchange Rate with China")
```


Holt method:

```{r}
hr1 <- holt(ExRatets)
summary(hr1)
```

BIC = 381.9494

```{r}
hr1f <- holt(ExRatets, h = 8, level = c(80, 95))
autoplot(hr1f) +
autolayer(fitted(hr1f), series="Fitted") +
ylab("Exchange Rate with China") + xlab("Year")
```


Holt-Winters method:

```{r}
hrw1 <- hw(ExRatets)
summary(hrw1)
```

BIC = 403.2346 


```{r}
hrw1f <- hw(ExRatets, h = 8, level = c(80, 95))
autoplot(hrw1f) +
autolayer(fitted(hrw1f), series="Fitted") +
ylab("Exchange Rate with China") + xlab("Year")
```


