---
title: "FDIGDP"
author: "Jesse Conway"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
Data <- read_excel("~/Desktop/FinalPaperR/UpdatedData.xls")
#View(Data)
library(forecast)
```

```{r}
FDIGDP <- Data[1:236,7]
FDIGDPts <- ts(data = FDIGDP, start = c(1960,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

FDIGDP2 <- Data[5:236,7]
FDIGDP2ts <- ts(data = FDIGDP2, start = c(1961,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)
```

ARIMA TESTING d = 0:

mean trend:

```{r}
R000mean <- Arima(FDIGDPts, order = c(0,0,0)) 
summary(R000mean)
```

BIC = -1513.12

linear trend:

```{r}
R000lt <- Arima(FDIGDPts, order = c(0,0,0), include.drift = TRUE) 
summary(R000lt)
```

BIC = -1630.4

trend + seasonal dummies:

```{r}
Sdum <- seasonaldummy(FDIGDPts)
R000sd <- Arima(FDIGDPts, order = c(0,0,0), include.drift = TRUE, xreg = Sdum) 
summary(R000sd)

```

BIC = -1617.92

trend + seasonal differences:

```{r}
R000sf <- Arima(FDIGDPts, order = c(0,0,0), seasonal = c(0,1,0), include.drift = TRUE) 
summary(R000sf)
```

BIC = -1509.04

compare w/ same sample size:

```{r}
R0002 <- Arima(FDIGDP2ts, order = c(0,0,0), include.drift = TRUE) 
summary(R0002)
```

BIC = -1630.4

best model:

```{r}
RESR00lt <- residuals(R000lt)
```

PAC's/ AC's:

```{r}

Acf(RESR00lt)
Pacf(RESR00lt)

```

AR(3)

ARIMA testing:

```{r}
Rar1 <- Arima(FDIGDPts, order = c(1,0,0), include.drift = TRUE) 
summary(Rar1)
```

BIC = -1647.48

```{r}
Rarma11 <- Arima(FDIGDPts, order = c(1,0,1), include.drift = TRUE) 
summary(Rarma11)
```

BIC = -1661.31

```{r}
Rma1 <- Arima(FDIGDPts, order = c(0,0,1), include.drift = TRUE) 
summary(Rma1)
```

BIC = -1638.6

```{r}
Rarma21 <- Arima(FDIGDPts, order = c(2,0,1), include.drift = TRUE) 
summary(Rarma21)
```

BIC = -1659.89

```{r}
Rarma12 <- Arima(FDIGDPts, order = c(1,0,2), include.drift = TRUE) 
summary(Rarma12)
```

BIC = -1658.82

So, ARMA(1,1) is our best model.

White noise?

```{r}
checkresiduals(Rarma11)
```

WHY IS IT NOT WHITE NOISE?

Forecast: QUESTION (what to forecast on)?

```{r}
plot(forecast(Rarma11,h=8))
for011 <- forecast(Rarma11, h = 8)
print(for011)
```

ARIMA TESTING d = 1:

Test for a unit root just to see


Let's run the KPSS and ADF tests:

```{r}
Rmean <- Arima(FDIGDPts, order = c(0,0,0)) 
ndiffs(RES_mean,test="kpss")
ndiffs(RES_mean,test="adf")
```

This implies that there is a unit root, so lets see how taking it out changes the BIC:

mean trend:

```{r}
R010mean <- Arima(FDIGDPts, order = c(0,1,0)) 
summary(R010mean)
```

BIC = -1555.2

linear trend:

```{r}
R010lt <- Arima(FDIGDPts, order = c(0,1,0), include.drift = TRUE) 
summary(R010lt)
```

BIC = -1549.76

trend + seasonal dummies:

```{r}
Sdum2 <- seasonaldummy(FDIGDPts)
R010sd <- Arima(FDIGDPts, order = c(0,1,0), xreg = Sdum2) 
summary(R010sd)

```

BIC = -1548.26

trend + seasonal differences:

```{r}
R010sf <- Arima(FDIGDPts, order = c(0,1,0), seasonal = c(0,1,0)) 
summary(R010sf)
```

BIC = -1384.38

compare w/ same sample size:

```{r}
R0102 <- Arima(FDIGDP2ts, order = c(0,1,0)) 
summary(R0102)
```

BIC = -1524.69

best model:

```{r}
RESR010mean <- residuals(R010mean)
```

PAC's/ AC's:

```{r}

Acf(RESR010mean)
Pacf(RESR010mean)

```


ARIMA testing:

```{r}
Rima11 <- Arima(FDIGDPts, order = c(0,1,1)) 
summary(Rima11)
```

BIC = -1653.45


```{r}
Rari11 <- Arima(FDIGDPts, order = c(1,1,0)) 
summary(Rari11)
```

BIC = -1633.05

```{r}
Rarima111 <- Arima(FDIGDPts, order = c(1,1,1)) 
summary(Rarima111)
```

BIC = -1649.27

```{r}
Rima12 <- Arima(FDIGDPts, order = c(0,1,2)) 
summary(Rima12)
```

BIC = -1648.94



So, MA(1) is our best model.

White noise?

```{r}
checkresiduals(Rima11)
```

White noise!

Forecast: QUESTION (what to forecast on and how many quarters out)?

```{r}
plot(forecast(Rima11,h=8))
for0112 <- forecast(Rima11, h = 8)
print(for0112)
```


* forecasts 2 years out?

SMOOTHING MODELS:

Plot:

```{r}
library(ggplot2)
autoplot(FDIGDPts) +
ylab("FDI/GDP") + xlab("Year")
```


Simple Smoothing:

```{r}
s1 <- ses(FDIGDPts, h = 8, level = c(80, 95), alpha = 0.1)
autoplot(s1) +
autolayer(fitted(s1), series="Fitted") +
ylab("FDI/GDP") + xlab("Year")
```


```{r}
s2 <- ses(FDIGDPts, h = 8, level = c(80, 95), alpha = 0.5)
autoplot(s2) +
autolayer(fitted(s2), series="Fitted") +
ylab("FDI/GDP") + xlab("Year")
```


```{r}
s3 <- ses(FDIGDPts, h = 8, level = c(80, 95), alpha = 0.9)
autoplot(s3) +
autolayer(fitted(s3), series="Fitted") +
ylab("FDI/GDP") + xlab("Year")
```

```{r}
ss4 <- ses(FDIGDPts)
 summary(ss4)
 
```

BIC = -1037.028
Alpha = 0.294 


```{r}
s4 <- ses(FDIGDPts, h = 8, level = c(80, 95))
autoplot(s4) +
autolayer(fitted(s4), series="Fitted") +
ylab("FDI/GDP")
```


Holt method:

```{r}
hr1 <- holt(FDIGDPts)
summary(hr1)
```

BIC = -1024.980 

```{r}
hr1f <- holt(FDIGDPts, h = 8, level = c(80, 95))
autoplot(hr1f) +
autolayer(fitted(hr1f), series="Fitted") +
ylab("FDI/GDP") + xlab("Year")
```


Holt-Winters method:

```{r}
hrw1 <- hw(FDIGDPts)
summary(hrw1)
```

BIC = -979.9366 


```{r}
hrw1f <- hw(FDIGDPts, h = 8, level = c(80, 95))
autoplot(hrw1f) +
autolayer(fitted(hrw1f), series="Fitted") +
ylab("FDI/GDP") + xlab("Year")
```





