---
title: "NXGDP"
author: "Jesse Conway"
date: "4/22/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
Data <- read_excel("~/Desktop/FinalPaperR/UpdatedData.xls")
#View(Data)
library(forecast)
```

```{r}
NXGDP <- Data[1:236,8]
NXGDPts <- ts(data = NXGDP, start = c(1960,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)

NXGDP2 <- Data[5:236,8]
NXGDP2ts <- ts(data = NXGDP2, start = c(1961,1), frequency = 4, end = c(2018,4)) # data start in 1960Q1 and end in 2018Q3)
```

ARIMA TESTING d = 0:

mean trend:

```{r}
R000mean <- Arima(NXGDPts, order = c(0,0,0)) 
summary(R000mean)
RES_mean = residuals(R000mean)
```

BIC = -1205.03

linear trend:

```{r}
R000lt <- Arima(NXGDPts, order = c(0,0,0), include.drift = TRUE) 
summary(R000lt)
```

BIC = -1487.06

trend + seasonal dummies:

```{r}
Sdum <- seasonaldummy(NXGDPts)
R000sd <- Arima(NXGDPts, order = c(0,0,0), include.drift = TRUE, xreg = Sdum) 
summary(R000sd)

```

BIC = -1470.78

trend + seasonal differences:

```{r}
R000sf <- Arima(NXGDPts, order = c(0,0,0), seasonal = c(0,1,0), include.drift = TRUE) 
summary(R000sf)
```

BIC = -1687.74

compare w/ same sample size:

```{r}
R0002 <- Arima(NXGDP2ts, order = c(0,0,0), include.drift = TRUE) 
summary(R0002)
```

BIC = -1458.05

best model:

```{r}
RESR00sf <- residuals(R000sf)
```

PAC's/ AC's:

```{r}

Acf(RESR00sf)
Pacf(RESR00sf)

```

MA(3) or AR(3)

ARIMA testing:

```{r}
Rma3 <- Arima(NXGDPts, order = c(0,0,3), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rma3)
```

BIC = -2021.6


```{r}
Rar3 <- Arima(NXGDPts, order = c(3,0,0), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rar3)
```

BIC = -1916.73

```{r}
Rarma11 <- Arima(NXGDPts, order = c(1,0,1), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rarma11)
```

BIC = -1918.82

```{r}
Rma2 <- Arima(NXGDPts, order = c(0,0,2), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rma2)
```

BIC = -1898.4

```{r}
Rma4 <- Arima(NXGDPts, order = c(0,0,4), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rma4)
```

BIC = -2024.18

```{r}
Rarma13 <- Arima(NXGDPts, order = c(1,0,3), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rarma13)
```

BIC = -2022.85

```{r}
Rma5 <- Arima(NXGDPts, order = c(0,0,5), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rma5)
```

BIC = -2019.74

```{r}
Rarma14 <- Arima(NXGDPts, order = c(1,0,4), seasonal = c(0,1,0), include.drift = TRUE) 
summary(Rarma14)
```

BIC = -2019.68

So, MA(4) is our best model.

White noise?

```{r}
checkresiduals(Rma4)
```

White noise!

Forecast: QUESTION (what to forecast on)?

```{r}
plot(forecast(Rma4,h=8))
for011 <- forecast(Rma4, h = 8)
print(for011)
```

ARIMA TESTING d = 1:

Test for a unit root just to see


Let's run the KPSS and ADF tests:

```{r}
Rmean <- Arima(NXGDPts, order = c(0,0,0)) 
ndiffs(RES_mean,test="kpss")
ndiffs(RES_mean,test="adf")
```

This implies that there is a unit root, so lets see how taking it out changes the BIC:

mean trend:

```{r}
R010mean <- Arima(NXGDPts, order = c(0,1,0)) 
summary(R010mean)
```

BIC = -2082.74

linear trend:

```{r}
R010lt <- Arima(NXGDPts, order = c(0,1,0), include.drift = TRUE) 
summary(R010lt)
```

BIC = -2077.99

trend + seasonal dummies:

```{r}
Sdum2 <- seasonaldummy(NXGDPts)
R010sd <- Arima(NXGDPts, order = c(0,1,0), xreg = Sdum2) 
summary(R010sd)

```

BIC = -2069.54

trend + seasonal differences:

```{r}
R010sf <- Arima(NXGDPts, order = c(0,1,0), seasonal = c(0,1,0)) 
summary(R010sf)
```

BIC = -1874.58

compare w/ same sample size:

```{r}
R0102 <- Arima(NXGDP2ts, order = c(0,1,0)) 
summary(R0102)
```

BIC = -2044.67

best model:

```{r}
RESR010mean <- residuals(R010mean)
```

PAC's/ AC's:

```{r}

Acf(RESR010mean)
Pacf(RESR010mean)

```


ARIMA testing:

```{r}
Rima11 <- Arima(NXGDPts, order = c(0,1,1)) 
summary(Rima11)
```

BIC = -2084.17


```{r}
Rari11 <- Arima(NXGDPts, order = c(1,1,0)) 
summary(Rari11)
```

BIC = -2083.34

```{r}
Rarima111 <- Arima(NXGDPts, order = c(1,1,1)) 
summary(Rarima111)
```

BIC = -2079.28

```{r}
Rima12 <- Arima(NXGDPts, order = c(0,1,2)) 
summary(Rima12)
```

BIC = -2079.29



So, MA(1) is our best model.

White noise?

```{r}
checkresiduals(Rima11)
```

White noise!

Forecast: QUESTION (what to forecast on and how many quarters out)?

```{r}
plot(forecast(Rima11,h=8))
for0112 <- forecast(Rima11, h = 8)
print(for0112)
```


* forecasts 2 years out?

SMOOTHING MODELS:

Plot:

```{r}
library(ggplot2)
autoplot(NXGDPts) +
ylab("NX/GDP") + xlab("Year")
```


Simple Smoothing:

```{r}
s1 <- ses(NXGDPts, h = 8, level = c(80, 95), alpha = 0.1)
autoplot(s1) +
autolayer(fitted(s1), series="Fitted") +
ylab("NX/GDP") + xlab("Year")
```


```{r}
s2 <- ses(NXGDPts, h = 8, level = c(80, 95), alpha = 0.5)
autoplot(s2) +
autolayer(fitted(s2), series="Fitted") +
ylab("NX/GDP") + xlab("Year")
```


```{r}
s3 <- ses(NXGDPts, h = 8, level = c(80, 95), alpha = 0.9)
autoplot(s3) +
autolayer(fitted(s3), series="Fitted") +
ylab("NX/GDP") + xlab("Year")
```

```{r}
ss4 <- ses(NXGDPts)
 summary(ss4)
 
```

BIC = -1461.962
Alpha = 0.9999


```{r}
s4 <- ses(NXGDPts, h = 8, level = c(80, 95))
autoplot(s4) +
autolayer(fitted(s4), series="Fitted") +
ylab("NX/GDP")
```


Holt method:

```{r}
hr1 <- holt(NXGDPts)
summary(hr1)
```

BIC = -1448.729 

```{r}
hr1f <- holt(NXGDPts, h = 8, level = c(80, 95))
autoplot(hr1f) +
autolayer(fitted(hr1f), series="Fitted") +
ylab("NX/GDP") + xlab("Year")
```


Holt-Winters method:

```{r}
hrw1 <- hw(NXGDPts)
summary(hrw1)
```

BIC = -1302.186


```{r}
hrw1f <- hw(NXGDPts, h = 8, level = c(80, 95))
autoplot(hrw1f) +
autolayer(fitted(hrw1f), series="Fitted") +
ylab("NX/GDP") + xlab("Year")
```












